---
title: "code book"
author: "basta"
date: "3/15/2021"
output: html_document
---

Feature Selection 
=================

	The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals time.acc.xyz and timegyro.xyz. These time domain signals were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (timebody.acc.xyz and timeGgavity.acc.xyz) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (timebody.acc.jerk.xyz and timebody.gyro.jerk.xyz). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (timebody.acc.mag, timegravity.acc.mag, timebody.accjerk.mag, timebody.gyro.mag, timebody.gyro.jerk.mag). 

Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing freqbody.acc.xyz, freqbody.acc.jerk.xyz, freabody.gyro.xyz, ferqbody.acc.jerk.mag, freqbody.gyro.mag, freqbody.gyro.jerk.mag . 

These signals were used to estimate variables of the feature vector for each pattern:  
'.xyz' is used to denote 3-axial signals in the X, Y and Z directions.

                  
timebody.acc.xyz
timegravity.acc.xyz
timebody.acc.jerk.xyz
timebody.gyro.xyz
timebody.gyro.jerk.xyz
timebody.acc.mag
timegravity.acc.mag
timebody.accjerk.mag
timebody.gyro.mag
timebody.gyro.jerk.mag
freqbody.acc.xyz
freqbody.acc.jerk.xyz
freabody.gyro.xyz
freqbody.acc.mag
ferqbody.acc.jerk.mag
freqbody.gyro.mag
freqbody.gyro.jerk.mag

The set of variables that were estimated from these signals are: 

mean(): Mean value
std(): Standard deviation

other variable used in tidy data is :

subject : refer to 30 volunteers within an age bracket of 19-48 years

activitylables : refer to six activities each person pergormed (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING)


The complete list of variables of each feature vector is available in 'features.txt'

=============================================================================================
here is a code to import,merge,rename variable,and get the mean for each variable from each activity and each subject
=============================================================================================

```{r }
# import library tidyvers
library(tidyverse)
# import data sets to R
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip",destfile = "./file1",method = "curl",mode = "wb")
# unzip data sets
unzip(zipfile = "./file1",exdir = "./file2")
# read the x_train data set
x_train <- read.table("./file2/UCI HAR Dataset/train/X_train.txt",header = FALSE,sep = "")
# read y_train data set
y_train <- read.table("./file2/UCI HAR Dataset/train/y_train.txt",header = FALSE,sep = "")
# read subject_train data set
subject_train <- read.table("./file2/UCI HAR Dataset/train/subject_train.txt",header = FALSE,sep = "")
# merge all data set relate to train and asign in to finaltrain
finaltrain <- cbind(subject_train,y_train,x_train)
# read y_test data set
y_test <- read.table("./file2/UCI HAR Dataset/test/y_test.txt",header = FALSE,sep = "")
# read x_test data set
X_test <- read.table("./file2/UCI HAR Dataset/test/X_test.txt",header = FALSE,sep = "")
# read subject_test data set
subject_test <- read.table("./file2/UCI HAR Dataset/test/subject_test.txt",header = FALSE,sep = "")
# merge all data set relate to test and asign in to finaltest
finaltest <- cbind(subject_test,y_test,X_test)
# merge finaltest and finaltrain 
mergeData <- rbind(finaltest,finaltrain)
# read features.txt
features <- read.table("./file2/UCI HAR Dataset/features.txt",header = FALSE,sep = "")
# names merge data column from 3:563 by features values
names(mergeData)[3:563] <- features[,2]
# names the second column in mergedata to avoid error in select later(am not sure ^_^)
names(mergeData)[2] <- "V2"
# select the first two column and any column contain(mean() or std())
measurements <- select(mergeData,c(1:2,contains('mean()')|contains('std()')))
# read activity_labels
activity_labels <- read.table("./file2/UCI HAR Dataset/activity_labels.txt",header = FALSE,sep = "")
# use activity_lables second column to replace the value in measurements second column
measurements$V2 <- as.factor(sapply(measurements$V2,function(x) activity_labels$V2[x]))
# replace any underscore in column names by ""
colnames(measurements) <- gsub("-","",x = colnames(measurements))
# replace any "tBody" in column names by "timebody."
colnames(measurements) <- sub("tBody","timebody.",x = colnames(measurements))
# replace any "fBody" in column names by "freqbody"
colnames(measurements) <- sub("fBody","freqbody.",x = colnames(measurements))
# replace any "tGravity" in column names by "timegravity."
colnames(measurements) <- sub("tGravity","timegravity.",x = colnames(measurements))
# replace any "Acc" in column names by "acc."
colnames(measurements) <- sub("Acc","acc.",x = colnames(measurements))
# replace any "Gyro" in column names by "gyro."
colnames(measurements) <- sub("Gyro","gyro.",x = colnames(measurements))
# replace any "Mag" in column names by "mag."
colnames(measurements) <- sub("Mag","mag.",x = colnames(measurements))
# replace any "Jerk" in column names by "jerk."
colnames(measurements) <- sub("Jerk","jerk.",x = colnames(measurements))
# replace any "X"in column names by "x"
colnames(measurements) <- sub("X","x",x = colnames(measurements))
# replace any "Y" in column names by "y"
colnames(measurements) <- sub("Y","y",x = colnames(measurements))
# replace any "Z" in column names by "z"
colnames(measurements) <- sub("Z","z",x = colnames(measurements))
# replace any "Body" in column names by "body"
colnames(measurements) <- sub("Body","body",x = colnames(measurements))
# rename first two column by "subject" and "activitylabels" respectivly
colnames(measurements)[1:2] <- c("subject","activitylabels")
# make independent tidy data set with the average of each variable for each activity and each subject.
tidydata <- measurements%>% group_by(subject,activitylabels) %>% summarise_each(funs = mean)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
